### 2009-09-10 trunk/latex/paper1/contents.tex
paper

Following the work by Milo et al. \cite{Milo2002}, similarity between two
networks can be measured by computing Pearson's correlation coefficient between
the corresponding TCPs, which yields a value between -1 (most dissimilar) and 1
(most similar):

@@

\begin{figure*}[!t]
\center
\subfigure[ref1][Software
network]{\includegraphics[width=2.5in]{triads-software}}
\hfil
\subfigure[ref2][Non-software network]{\includegraphics[width=2.5in]{triads-nonsw}%
}
\caption{Triad profiles}
\label{fig:profiles}
\end{figure*}

@@

\subsubsection{BCR+}

@@

\subsubsection{LF}

@@

\subsubsection{CGW}

@@

\begin{figure*}[!t]
\center

\subfigure[Software network]{\includegraphics[width=1.0in]{hist-cgw}}

\subfigure[Non-software network]{\includegraphics[width=1.0in]{hist-bcr}}

\subfigure[Non-software network]{\includegraphics[width=1.0in]{hist-lf}}

\caption{Triad profiles}
\label{fig:histograms}
\end{figure*}

>>>>

Following the work by Milo et al. \cite{Milo2004}, similarity between two
networks can be measured by computing Pearson's correlation coefficient between
the corresponding TCPs, which yields a value between -1 (most dissimilar) and 1
(most similar):

@@

% Word adjacency network: word Y follows word X => X->Y
%\begin{figure*}[!t]
%\center
%\subfigure[ref1][Software
%network]{\includegraphics[width=2.5in]{triad-jabref}}
%\hfil
%\subfigure[ref2][Non-software network]{\includegraphics[width=2.5in]{triad-lang}%
%}
%\caption{Triad profiles}
%\label{fig:profiles}
%\end{figure*}

\begin{figure}[!t]
\center
\includegraphics{tcp}

\caption{Triad concentration profiles (TCP) for two networks. On the left,
network extracted from the software system JabRef (see Appendix A). On the
right, word adjacency network for the Japanese language \cite{Milo2004}.}
\label{fig:profiles}
\end{figure}

@@

\subsection{BCR+ networks}

@@

\subsection{LF networks}

@@

\subsection{CGW networks}

@@

%\begin{figure*}[!t]
%\center
%
%\subfigure[CGW]{\includegraphics[width=1.0in]{hist-cgw}}
%
%\subfigure[BCR+]{\includegraphics[width=1.0in]{hist-bcr}}
%
%\subfigure[LF]{\includegraphics[width=1.0in]{hist-lf}}
%
%\caption{Triad profiles}
%\label{fig:histograms}
%\end{figure*}
